### 2018-09-13 Paper/Paper.tex
Updated model section

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
%\usepackage{hyperref}
\usepackage{biblatex}

@@

\section{Model}
Each component of the laser is treated separately and all processes will be composed to represent a single circuit of the laser.

\subsection{Gain}
As the pulse travels through the gain media the change in energy is
\begin{align*}
\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es},
\end{align*}
where $g_0$ is a small signal gain, and $E_{sat}$ is the energy at which the gain starts to saturate \cite{silfvast}. For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly. The energy can be solved analytically by separating and integrating yielding
\begin{align}
\label{eq:energy}
E(z) = \Es W_0 \left( \frac{E_0}{\Es} e^{E_0 / \Es} e^{g_0 z} \right),
\end{align}
where $W_0$ is the Lambert $W$ function. However, only the exiting energy is of interest, thus \eqref{eq:energy} can be written as
\begin{align*}
E' = \Es W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right),
\end{align*}
where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain media. Since the energy can be expressed as
\begin{align*}
E &= \int_{-\infty}^{\infty} |A(T)|^2 dT,
\end{align*}
it can be shown that
\begin{align*}
\frac{E'}{E} &= \left( \frac{A'}{A} \right)^2,
\end{align*}
and so the gain in terms of the amplitude is given by
\begin{align}
\label{eq:gain}
G(A) &= \left[ \frac{\Es}{E} W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right) \right]^{1/2} A.
\end{align}

\subsection{Dispersion}
Expressions for the amplitude as the pulse travels through the grating as well as the fibre can be derived from
\begin{align}
\label{eq:nlse}
i \pdiff{A}{z} - \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \gamma |A|^2 A = 0,
\end{align}
the non-linear Schr\"{o}dinger equation \cite{ferreira}. In the case of the dispersive element $\gamma$ is assumed to be negligible. Thus, \eqref{eq:nlse} reduces to
\begin{align*}
i \pdiff{A}{z} - \frac{1}{2} \beta_2 \pdiff[2]{A}{T} &= 0,
\end{align*}
and after taking the Fourier transform
\begin{align*}
\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
\end{align*}
The Fourier transform of $A$ can be found and evaluated at $z = L_d$ yielding
\begin{align*}
D(A) &= \FTi{e^{\frac{1}{2} i \beta_2 \omega^2 L_D} \FT{A}}
\end{align*}
as the effect of the dispersive element on the pulse.

\subsection{Fibre}
The effect of the fibre can also be found from \eqref{eq:nlse}, by assuming the dispersion of the fibre is negligible when compared to the dispersive element the non-linear Schr\"{o}dinger equation simplifies to
\begin{align*}
\pdiff{A}{z} - i \gamma |A|^2 A = 0,
\end{align*}
or after multiplying by the complex conjugate of $A$,
\begin{align}
\label{eq:fibre}
\pdiff{A}{z}\bar{A} - i \gamma |A|^4 = 0.
\end{align}
Adding \eqref{eq:fibre} to its complex conjugate gives
\begin{align}
\label{eq:fibre2}
\pdiff{|A|^2}{z} &= 0,
\end{align}
this suggests the envelope of the pulse does not change as it travels through the fibre, a solution of the form $A = A_0 e^{i \varphi}$ can be assumed. Substituting this expression into \eqref{eq:fibre2} gives $\varphi = \gamma |A|^2 z$ therefore
\begin{align*}
F(A) &= A e^{i \gamma |A|^2 L_f},
\end{align*}
where $L_f$ is the length of the fibre.

\subsection{Loss}
Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit. It will be assumed all loss occurs at a particular point in the circuit, however, the model can easily be modified to account for the optical loss between each component. The loss is then given as
\begin{align*}
L(A) &= C e^{- \alpha L}A,
\end{align*}
where $C$ is the loss due to the output coupler, and $\alpha$ is a characteristic loss per length of the fibre.

\subsection{Modulation}
Pick
\begin{align*}
M(A) &= e^{-T^2 / 2 T_M^2} A
\end{align*}
since its Fourier transform is itself

@@

\newpage
\appendix
\section{Numbers}

\begin{table}
\begin{tabular}{|l|l|}
\hline
Parameter & Value \\
\hline
$\beta_2^g L_D$ & $10$--$2000 \text{ps}^2$ \\
$g_0$ & $1$--$10 \text{m}^{-1}$ \\
$\beta_2^f$ & $20$--$50 \text{ps}^2/ \text{km}$ \\
$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \\
$\Es$ & $10^4 \text{pJ}$ \\
$L_g$ & $3 \text{m}$ \\
\hline
\end{tabular}
\end{table}

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{biblatex}

@@

\section{Model}
The laser cavity is treated as the composition of five independent process---gain, nonlinearity, loss, dispersion, and modulation. Expressions for each component will be derived from the  generalized nonlinear Schr\"{o}dinger equation \cite{agrawal, ferreira, shtyrina, yarutkina},
\begin{align}
\label{eq:nlse}
\pdiff{A}{z} = - i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
\end{align}
where $A$ is the complex amplitude of the pulse, $\beta_2$ and $\beta_3$ are the second and third order dispersion coefficients respectively, $\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fiber.

\subsection{Gain}
Within the Er-doped gain fiber the other four processes are assumed to be negligible, and so \eqref{eq:nlse} reduces to
\begin{align}
\label{eq:gainde}
\pdiff{A}{z} = \frac{1}{2} g(A) A
\end{align}
with
\begin{align*}
g(A) &= \frac{g_0}{1 + E / \Es},
\end{align*}
where $g_0$ is a small signal gain, $\Es$ is the energy at which the gain begins to saturate, and \begin{align*}
E = \int_{-\infty}^\infty |A|^2 \, dT,
\end{align*}
is the energy of the pulse \cite{bohun, yarutkina}. We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. Taking
\begin{align*}
\pdiff{A}{z} = \frac{1}{2} \cdot \frac{g_0 A}{1 + E / \Es},
\end{align*}
multiplying by $\bar{A}$, the complex conjugate of $A$, and then adding the complex conjugate gives
\begin{align*}
\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es},
\end{align*}
which after integrating becomes
\begin{align*}
\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
\end{align*}
For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly. A closed form of the energy can be found by separating and integrating yielding
\begin{align}
\label{eq:energy}
E(z) = \Es W_0 \left( \frac{E_0}{\Es} e^{E_0 / \Es} e^{g_0 z} \right),
\end{align}
where $W_0$ is the Lambert $W$ function. However, only the exiting energy is of interest, thus \eqref{eq:energy} can be written as
\begin{align*}
E' = \Es W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right),
\end{align*}
where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain fiber. Since $E \sim |A|^2$ the gain in terms of the amplitude is given by
\begin{align}
\label{eq:gain}
G(A) &= \left[ \frac{\Es}{E} W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right) \right]^{1/2} A.
\end{align}

\subsection{Nonlinearity of Fiber}
The effect of the nonlinearity of the fiber can also be found from \eqref{eq:nlse}:
\begin{align*}
\pdiff{A}{z} - i \gamma |A|^2 A = 0,
\end{align*}
which similarly to the gain, can be transformed by multiplying by the complex conjugate of $A$, and adding its complex conjugate gives
\begin{align}
\label{eq:fibre}
\pdiff{|A|^2}{z} &= 0.
\end{align}
This suggests the envelope of the pulse does not change as it travels through the fiber---a solution of the form $A = A_0 e^{i \varphi}$ can be assumed. Substituting this expression into \eqref{eq:fibre} gives $\varphi = \gamma |A|^2 z$ therefore
\begin{align*}
F(A) &= A e^{i \gamma |A|^2 L_f},
\end{align*}
where $L_f$ is the length of the fiber.

\subsection{Loss}
Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit. It will be assumed all loss occurs at a particular point in the circuit because of the extremely high reflectivity of the fiber the optical loss is negligible compared to the output coupler loss ***cite. The loss is then given as
\begin{align*}
L(A) &= C e^{- \alpha L}A,
\end{align*}
where $C$ is the loss due to the output coupler.

\subsection{Dispersion}
The dominant dispersion is due to the chirped fiber Bragg grating (CFBG)---the dispersion due to the fiber is negligible in comparison \cite{agrawalother}. The dispersive pieces of \eqref{eq:nlse} give
\begin{align}
\label{eq:disp}
\pdiff{A}{z} = -i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T},
\end{align}
but, the third order effects of dispersion will be neglected ***cite. Although, under some circumstances they may need to be considered since the CFBG is highly dispersive \cite{litchinitser}. Taking the Fourier transform of \eqref{eq:disp} gives
\begin{align*}
\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
\end{align*}
The Fourier transform of $A$ can be found by integrating and
\begin{align*}
D(A) &= \FTi{e^{i \frac{1}{2} \beta_2 \omega^2 L_D} \FT{A}}
\end{align*}
is the effect of the CFBG on the pulse.

\subsection{Modulation}
Pick a function that is bump-like, infinitely differentiable (I don't know how important that is), and has a maximum of $1$. We shall pick
\begin{align*}
M(A) &= e^{-T^2 / 2 T_M^2} A,
\end{align*}
where $T_M$ is a characteristic width of the modulation, since its Fourier transform is itself. ***I don't know how to write this.

\subsection{Combining the Pieces}

\begin{align*}
\mathcal{L}(A) = M(D(L(F(G(A)))))
\end{align*}

A solution such that $|\mathcal{L}(A)|^2 = |A|^2$ is sought.

@@

\begin{table}
\begin{tabular}{|l|l|}
\hline
Parameter & Value \\
\hline
$\beta_2^g L_D$ & $10$--$2000 \text{ps}^2$ \\
$g_0$ & $1$--$10 \text{m}^{-1}$ \\
$\beta_2^f$ & $20$--$50 \text{ps}^2/ \text{km}$ \\
$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \\
$\Es$ & $10^4 \text{pJ}$ \\
$L_G$ & $3 \text{m}$ \\
\hline
\end{tabular}
\end{table}
